\section{ENTER THE SINGULARITY}

\begin{center}
   \textbf{ECLIPSE PHASE}

   An "eclipse phase" is the period of time between when a cell is infected by
   a virus and when the virus appears within the cell and transforms it. During
   this period, the cell does not appear to be infected, but it is.
\end{center}


We humans have a special way of pulling ourselves up and kicking ourselves down
at the same time. We'd achieved more progress than ever before, at the cost of
wrecking our planet and destabilizing our own governments. But things were
starting to look up.

With exponentially accelerating technologies, we reached out into the solar
system, terraforming worlds and seeding new life. We re-forged our bodies and
minds, casting off sickness and death. We achieved immortality through the
digitization of our minds, resleeving from one biological or synthetic body to
the next at will. We uplifted animals and AIs to be our equals. We acquired
the means to build anything we desired from the molecular level up, so that no
one need want again.

Yet our race toward extinction was not slowed, and in fact received a
machine-assist over the precipice. Billions died as our technologies rapidly
bloomed into something beyond control ... further transforming humanity into
something else, scattering us throughout the solar system, and reigniting
vicious conflicts. Nuclear strikes, biowarfare plagues, nanoswarms, mass
uploads ... a thousand horrors nearly wiped humanity from existence.

We still survive, divided into a patchwork of restrictive inner system
hypercorp-backed oligarchies and libertarian outer system collectivist
habitats, tribal networks, and new experimental societal models. We have
spread to the outer reaches of the solar system and even gained footholds in
the galaxy beyond. But we are no longer solely "human" ... we have evolved
into something simultaneously more and different -- something
\textbf{transhuman}.

\begin{quote}
   \textbf{What is Transhumanism?}

   Transhumanism is a term used synonymously to mean "human enhancement".
   It is an international cultural and intellectual movement that endorses the
   use of science and technology to enhance the human condition, both mentally
   and physically. In support of this, transhumanism also embraces using
   emerging technologies to eliminate the undesirable elements of the human
   condition such as aging, disabilities, diseases, and involuntary death. Many
   transhumanists believe these technologies will be arriving in our near future
   at an exponentially accelerated pace and work to promote universal access to
   and democratic control of such technologies. In the long scheme of things,
   transhumanism can also be considered the transitional period between the
   current human condition and an entity so far advanced in capabilities (both
   physical and mental faculties) as to merit the label "posthuman".

   As a theme, transhumanism embraces heady questions. What defines human? What
   does it mean to defeat death? If minds are software, where do you draw the
   line with programming them? If machines and animals can also be raised to
   sentience, what are our responsibilities to them? If you can copy yourself,
   where does "you" end and someone new begin? What are the potentials of these
   technologies in terms of both oppressive control and liberation? How will
   these technologies change our society, our cultures, and our lives?
\end{quote}

\begin{center}
   Your mind is software. \emph{Program it.}\\
   Your body is a shell. \emph{Change it.}\\
   Death is a disease. \emph{Cure it.}\\
   Extinction is approaching. \emph{Fight it.}\\
\end{center}


\section{ECLIPSE PHASE UNIVERSE}

\subsection{Eclipse Phase Factions}

One would have thought a cataclysmic event such as the Fall would bring
surviving transhumanity closer to each other in an attempt to jointly
dedicate themselves to the repopulation of the solar system and continued
prosperity. While some of the post-Fall economic, social, or political powers
do indeed pursue philanthropic or altruistic agendas, the remoteness and
physical isolation of transhuman colonies and habitats stretched across the
solar system, the disembodiment of the infomorph refugees, and the ubiquity of
the mesh's myriad of memes and ideologies have promoted the evolution of a
wide spectrum of philosophies, agendas, and political models. Today,
transhumanity couldn't be further from walking a united path toward its future.

\subsection{The Hypercorps} 

The hypercorps both evolved from and superseded the old earthbound
transnational corporations, economic giants whose influence (direct or covert)
extended into the governments and nations of old. The transformation of some
of those monolithic transnationals into the slimmer, future-embracing, more
flexible and faster hypercorps known today preceded the Fall and allowed these
financial sharks to adapt to transhumanity's challenges and navigate the
swiftly changing economic waters rapidly and efficiently.

Most hypercorps are decentralized, non-asset-based legal entities (sometimes
entirely virtual) relying on an intricate system of specialized internal
subsidiaries and partner companies to develop, produce, and market their
products and services. Nearly complete automation, advanced robotics, morph
technology, mesh networking, and cornucopia machines allow the hypercorps to
abstain from mass employment for labor or production. Many administrative
tasks are performed in virtual environments and simulated offices. The need
for physical labor has mostly been reduced to tasks associated with habitat
construction or deep-space mining, which benefit heavily from the
overabundance of infomorph refugees desperate to regain a physical presence. 

\subsection{Political Factions} 

Transhumanity's social, cultural, and ideological diversity, as well as its
scattered and isolated presence in habitat clusters throughout the solar
system, allowed the manifestation of a wide range of political ideologies and
factions that advocate equally diverse models or systems. Naturally,
controversial regimes don't achieve stability overnight or evolve without
dissent, and even established ideologies over time rarely remain free of
diluting or even corrupting influence from outside factors or groups seeking
to promote their own agendas.

\subsection{The Mesh}

The mesh, as it exists in Eclipse Phase, is only possible thanks to major
developments made in computer/communication technologies and nanofabrication.
Wireless radio transceivers are so unobtrusively tiny that they can literally
be factored into anything. As a result, everything is computerized and
connected.

Data storage technology has advanced so that even an individual user's surplus
storage capacity can maintain an amount of information surpassing the entire
20th-century internet. Lifeloggers literally record every moment of their life
and never fear about running out of room.

Processing capabilities also exist at hyper-efficient levels. Modest handheld
devices can fulfill almost all of your needs, even while simultaneously running
a personal AI assistant, downloading media, uploading porn, and scanning
thousands of newsfeeds. Within the mesh network, devices that near their
processing limits simply share the burden with devices around them.

Similarly, transmission capacity now far exceeds most citizens' definition
of need. Anyone born within the last several generations has always lived in a
world in which hyper-realistic, multi-sensory media of nearly any length is
available for instantaneous download. Massive databases and archives are
copied back and forth with ease. Bandwidth is such a non-issue that most
people forget it ever was. The mesh is also never down. As a decentralized
network, if any one device is taken offline, connections merely route around
it, finding a path via thousands of available nodes.

Almost everyone is equipped with implanted personal computers, directly wired
to the user's cerebral functions. Thought-to-communication emulations enables
the user to control the implant just by thinking and to communicate without
vocalizing. Input is transmitted directly into the brain and sometimes
perceived as augmented reality, overlaid on the user's physical senses.

\begin{quote}
   \textbf{Hypercorps}

   The following is a small sampling of hypercorps.

   \textbf{ComEx}

   Comet Express specializes in delivery services, interstellar logistics,
   supply chains, and shipping. They maintain a presence on almost every
   transhuman habitat in the solar system, often via local subcontractors.
   ComEx maintains orbital hubs equipped with slingshot accelerators at
   strategic waypoints throughout the system and a fleet of cargo vessels
   and courier drones.


   \textbf{Direct Action}

   This apolitical mercenary corp, descended from the remnants of several
   pre-Fall militaries, provides security and public police services to
   self-governing habitats or hypercorp installations.


   \textbf{Ecologene}

   Ecologene specializes in genetically-engineered bio-architecture and
   environmental nanotech with a strong ecologically-conscious approach.


   \textbf{Fa Jing}

   Fa Jing dominates mining and energy production with a business philosophy
   that emphasizes network-building and social responsibility-sharing.


   \textbf{Gatekeeper Corporation}

   Born from the merger of several scientific institutions and their corporate
   financiers, this hypercorp made a name for itself when it decoded and opened
   the wormhole gateway discovered on Saturn's Pandora moon. The consortium
   today funds gatecrasher explorations through the Pandora Gate.


   \textbf{Skinthetic}

   Specializing in neogenesis and extensive, radical bio-modifications, this
   anarcho-capitalist company pushes the envelope of cloning, genetics, and
   morph design.


   \textbf{Solaris} 

   Solaris is the system's leading banking and financial investment hypercorp,
   dealing in insurances, futures markets, info-brokerage and high-risk
   investments. Solaris is a virtual corporation, with each banker acting as
   a nomadic office.
\end{quote}

\begin{quote}

   \textbf{\emph{Eclipse Phase Timeline}}


   All dates are given in reference to the Fall. BF = Before the Fall.
   AF = After the Fall. (e.g., BF 10 = 10 years before the Fall.)


   BF 60+
   \begin{itemize}
      \item Crisis grips the globe in the form of drastic climate changes,
         energy shortages, and geopolitical instability.
      \item Initial space expansion creates stations at the Lagrange Points
         , Luna, and Mars, with robotic exploration of the entire system.
      \item Construction begins on a space elevator.
      \item Medical advances improve health and organ repair. The rich pursue
         gene-fixing and transgenic pets.
      \item Computer intelligence capabilities equal and exceed that of the
         human brain. True AI not yet developed.
      \item Robotics become widespread and start to replace/invalidate many jobs.
      \item Modern nations expand their high-speed wireless networks.
   \end{itemize}


   BF 60-40
   \begin{itemize}
      \item Efforts to undertake mega-scale geoengineering on Earth cause as
         many problems as they fix.
      \item Major colonies established on the Moon and Mars; outposts
         established near Mercury, Venus, and the Belt. Explorers reach Pluto.
      \item First space elevator on Earth finished. Two others in progress.
         Space traffic booms.
      \item Mass driver built on the Moon.
      \item Terraforming of Mars begins.
      \item Fusion power developed and working plants established.
      \item Genetic enhancements, gene therapies (for longevity), and
         cybernetic implants become available to the wealthy and powerful.
      \item First non-autonomous AIs are secretly developed and quickly put
         to use in research and netwar.
      \item Experience playback (XP) technology developed and put into public
         use.
   \end{itemize}


   BF 40-20
   \begin{itemize}
      \item Violence and destabilization wrack the Earth; some conflicts
         spread into space.
      \item Argonauts split from hypercorps, taking resources to autonomist
         habitats.
      \item Space expansion opens up legal/ethical loopholes for tech
         development and allows for increased direct human experimentation.
      \item Human cloning becomes possible and available in some areas.
      \item Development of first transhuman species.
      \item First dolphins and chimpanzees uplifted to sapience.
      \item Fusion-drive spacecraft enter common usage.
      \item Extended colonization and terraforming of Mars continues. Belt and
         Titan colonized. Stations established throughout the system.
      \item The starving masses volunteer themselves for indentured servitude
         on hypercorp space projects.
      \item Augmented reality becomes widespread.
      \item Most networks transformed into self-repairing mesh networks.
      \item Personal AI aides become widespread.
   \end{itemize}


   BF 20-0
   \begin{itemize}
      \item Earth continues to suffer, but the pace of technology allows
         for some interesting developments.
      \item Expansion throughout the system, even into the Kuiper Belt.
      \item Transhuman species become widespread.
      \item Nanotech assemblers become available, but are strictly controlled
         and jealously guarded by the elite and powerful.
      \item Uploading and the digital emulation of memory and consciousness
         made possible.
      \item More species (gorillas, orangutans, octopi, ravens, parrots)
         uplifted to sapience.
      \item Pods see common usage, amid some controversy.
   \end{itemize}


   The Fall
   \begin{itemize}
      \item The TITANs evolve from a high-level distributed netwar experiment
         into self-improving seed AIs. For the first few days, their existence
         is unsuspected. They advance their awareness, knowledge, and power
         exponentially, infiltrating the mesh both on Earth and around the system.
      \item Large-scale netwar incursions break out between rival states on
         Earth, sparking numerous conflicts. These attacks are later blamed on
         the TITANs.
      \item Simmering tensions on Earth escalate into outright hostilities
         and warfare.
      \item Massive netwar breaks out and major systems crash as TITANs begin
         open attacks, also using autonomous war machines.
      \item Conflict quickly spirals out of control. The use of nuclear,
         biological, chemical, digital, and nanotech weapons reported by all sides.
      \item TITANs engage in mass forced uploading of human minds.
      \item TITAN attacks expand to other parts of solar system, heaviest on
         the Moon and Mars. Numerous habitats also fall.
      \item TITANs suddenly disappear from system, taking millions of uploaded
         minds with them.
      \item The Earth is left a devastated wasteland, a patchwork of radiation
         hotspots, sterile zones, nanoswarm clouds, roaming war machines, and
         other unknown and hidden things among the ruins.
   \end{itemize}


   AF 0-10
   \begin{itemize}
      \item A wormhole gateway is discovered on Saturn's moon Pandora, left by
         the TITANs. Four others are later found (in the Vulcanoids, on Mars,
         on Uranus, and in the Kuiper Belt); these are collectively referred
         to as "Pandora Gates".
      \item Expeditions are sent to extrasolar worlds via the Pandora Gates.
         Numerous exoplanet colonies established.
      \item First contact with the aliens known as the Factors shocks the
         system. Claiming to act as ambassadors for other alien civilizations,
         they provide little information about life outside the solar system
         and warn transhumans away from both seed AI and the Pandora Gates.
      \item An attempt to raise a generation of children using force-grown
         clones and time-accelerated VR fails miserably when most of the
         children die or go insane. Dubbed the Lost Generation, the survivors
         are viewed with repugnance and pity.
   \end{itemize}


   AF 10
   \begin{itemize}
      \item Present day.
   \end{itemize}
\end{quote}


\begin{quote}
   \textbf{socio-political entities}


   \textbf{Argonauts}

   The Argonauts are an open organization of techno-progressives that advocate
   the socially responsible use of technology. The Argonauts offer
   consultation services to political and economic powers throughout the
   solar system, but otherwise strictly refuse to be drawn into the solar
   system's political affairs.

   Memes: Information freedom, social responsibility, technological advancement

   Major Stations: Mitre Station (Lunar Orbit), Pelion Station (Kuiper Belt) 


   \textbf{Autonomists}

   The Autonomists are a loose alliance of several libertarian factions -- 
   anarcho-communists, anarcho-capitalists, and techno-socialists -- that
   promote egalitarian social models based on the pillars of direct democracy,
   individual/collective empowerment, social networks and reputation-building,
   and economic communism enabled by equal access to cornucopia machines,
   shared resources, and new technologies.

   Memes: Anarchism/Communism, Morphological Freedom

   Major Stations: Extropia (Belt), Locus (Trojans), Titan


   \textbf{Jovian Republic}

   A coup staged during the Fall brought a group of stations and habitats
   under military control and the Jovian Republic -- also known as the Jovian
   Junta -- was born. The Republic's authorities take a bio-conservative
   stance against many transhuman technologies and strictly control
   information channels and travel.

   Memes: Bio-conservatism, Nationalism, Security

   Major Stations: Liberty (Ganymede)


   \textbf{Planetary Consortium}

   The Planetary Consortium is an alliance of hypercorporate interests that
   jointly controls a number of stations and habitats, particularly in the
   inner system. The Consortium maintains a facade of democratic rule,
   facilitated by real-time online referendum voting, but it is an open secret
   that the hypercorps call the shots.

   Memes: Corporatism, Cyberdemocracy, Gerontocracy

   Main Stations: Progress (Deimos) , Elysium (Mars)


   \textbf{Scum}

   The derogative term "scum" describes large tribes of nomadic space gypsies,
   travelling from station to station in heavily modified barges or swarms of
   smaller space vessels, mostly former colonial ships. Part traveling
   carnival, part black market, the scum openly embrace body modification
   and experimentation.

   Memes: Lifestylism, Morphological freedom


   \textbf{Ultimates}

   This controversial faction uses applied eugenics to further its goal, the
   development of the ultimate transhuman species. Aside from sophisticated
   reprogenetic engineering and strict psychological training, their culture
   visualizes life in the universe as an evolutionary battle for survival and
   is built around the victory of the superior transhuman over its peers.

   Memes: Asceticism, Eugenics, Objectivism

   Major Stations: Xiphos (Uranus)
\end{quote}


\section{TERMINOLOGY}

\begin{itemize}
   \item \textbf{AGI:} Artificial General Intelligence. An AI that has cognitive
      faculties comparable to that of a human or higher. Aka "strong AI"
      (differentiating from "seed AI" or more specialized "weak AI".

   \item \textbf{AI:} Artificial Intelligence. Generally used to refer to weak
      AIs; i.e., AIs that do not encompass (or in some cases, are completely
      outside of) the full range of human cognitive abilities. AIs differ from
      AGIs in that they are usually specialized and/or intentionally
      crippled/limited.

   \item \textbf{AR:} Augmented Reality. Information from the mesh (universal
      data network) that is overlaid on your real-world senses. AR data is
      usually entoptic (visual), but can also be audio, tactile, olfactory,
      kinesthetic (body awareness), emotional, and other senses.

   \item \textbf{Bots:} Robots.

   \item \textbf{Brinkers:} Exiles who live on the fringes of the system,
      as well as other isolated and well-hidden nooks and crannies. Aka
      isolates, fringers, drifters.

   \item \textbf{Cornucopia Machine:} A nanofabricator.

   \item \textbf{Cortical Stack:} An implanted memory cell used for ego
      backup. Located where the spine meets the skull; can be cut out.

   \item \textbf{Ecto:} Personal mesh devices that are flexible,
      stretchable, self-cleaning, translucent, and solar-powered. From
      ecto-link (external link).  

   \item \textbf{Ego:} The part of you that switches from body to body.
      Aka ghost, soul, essence, spirit, persona.  

   \item \textbf{Ego-casting:} Term for sending egos via farcasting.  

   \item \textbf{Entoptics:} Augmented-reality images that you "see" in your
      head. ("Entoptic" means "within the eye".) 

   \item \textbf{Factors:} The alien ambassadorial race that deals with
      transhumanity. Aka Brokers.  

   \item \textbf{The Fall:} The apocalypse; the singularity and wars that
      nearly brought about the downfall of transhumanity.  

   \item \textbf{Farcasting:} Interstellar communication via FTL links.  

   \item \textbf{Firewall:} The secret conspiracy that works to protect
      transhumanity from "existential threats" (risks to transhumanity's
      continued existence).  

   \item \textbf{Flats:} Baseline humans (not genetically modified). Aka norms.

   \item \textbf{FTL:} Faster-Than-Light.  

   \item \textbf{Gate Crashers:} Explorers who take their chances using a
      Pandora Gate to go somewhere previously unexplored.  

   \item \textbf{Iktomi:} The name given to the mysterious alien race whose
      relics have been found beyond the Pandora gates.

   \item \textbf{Infomorph:} A digitized ego; a virtual body. Aka datamorphs,
      uploads, backups.

   \item \textbf{Infugee:} "Infomorph refugee", or someone who left everything
      behind on Earth during the Fall -- even their own body.

   \item \textbf{Isolates:} Those who live in isolated communities far outside
      the system (in the Kuiper Belt and Oort Cloud); aka outsters, fringers.  

   \item \textbf{Lost Generation:} In an effort to repopulate post-Fall, a
      generation of children were reared using forced-growth methods. The
      results were disastrous: many died or went insane, and the rest were
      stigmatized.  

   \item \textbf{Mercurials:} The non-human sentient elements of the
      transhuman "family", including AIs and uplifted animals.  

   \item \textbf{Mesh:} The omnipresent wireless mesh data network. Also used
      as a verb (to mesh) and adjective (meshed or unmeshed).  

   \item \textbf{Morph:} A physical body. Aka suit, jacket, sleeve, form.  

   \item \textbf{Muse:} Personal AI helper programs.  

   \item \textbf{Neo-Avians:} Uplifted ravens and gray parrots.  

   \item \textbf{Neo-Hominids:} Uplifted chimpanzees, gorillas, and orangutans.  

   \item \textbf{Pandora Gates:} The wormhole gateways left behind by the TITANs.  

   \item \textbf{Pods:} Mixed biological-synthetic morphs. Pod clones are
      force-grown and feature computer brains. Aka bio-bots, skinjobs,
      replicants. From "pod people".  

   \item \textbf{Reclaimers:} A transhuman faction that seeks to lift the
      interdiction and reclaim Earth.  

   \item \textbf{Reinstantiated:} Refugees from Earth who escaped only as
      bodiless infomorphs but have since been resleeved.  

   \item \textbf{Resleeving:} Changing bodies. Aka morphing, reincarnation,
      shifting, rebirthing.  
   \item \textbf{Seed AI:} An AGI that is capable of recursive
      self-improvement, allowing it to reach god-like levels of intelligence.  

   \item \textbf{Shell:} A synthetic physical morph. Aka synthmorph.

   \item \textbf{Singularity:} A point of rapid, exponential, and recursive
      technological progress, beyond which the future becomes impossible to
      predict. Often used to refer to the ascension of seed AIs to god-like
      levels of intelligence.  

   \item \textbf{Skin:} A biological physical morph. Aka meat, flesh.  

   \item \textbf{Splicers:} Genetically modified to eliminate genetic
      diseases and some other traits. Aka genefixed, cleangenes, tweaks.  

   \item \textbf{Synthmorph:} Synthetic morph. A robotic shell possesseds by
      a transhuman ego.

   \item \textbf{TITANs:} The human-created, recursively improving military
      AGIs that underwent a singularity and prompted the Fall. Original
      military designation was TITAN: Total Information Tactical Awareness
      Network.  

   \item \textbf{Transhuman:} An extensively modified human.

   \item \textbf{Uplifting:} Genetically transforming an animal species to
      sapience.  

   \item \textbf{Xenomorph:} Alien life form.  

   \item \textbf{XP:} Experiencing someone else's sensory input (in real-time
      or recorded). Aka experia, sim, simsense, playback.  

   \item \textbf{X-Risk:} Existential risk. Something that threatens the very
      existence of transhumanity.  
\end{itemize}

\begin{quote}
   \textbf{An Exsurgent Threat?}

   [Incoming Message. Source: Anonymous]

   [Public Key Decryption Complete]

   Ok, you asked, so I'll tell you. There are some elements within Firewall
   that don't buy into the TITANs-ran-amok-and-considered-us-a-threat idea,
   or even that the TITANs are solely responsible for the Fall. These people
   think that the TITANs found or encountered something when they started
   their takeoff toward the singularity -- something that changed them. They
   point to the wide range of multi-vector virii that ran loose during the
   Fall, and how even many of the TITANs seem to have succumbed to these
   infections. They also reference a disturbing number of accounts of events
   during the Fall that are inexplicable ... things like people being
   transformed into strange, alien creatures ... or phenomena that seem to
   defy certain physical laws, as if something was at times ignoring what we
   know of physics and just doing whatever it felt like ... Some of these
   voices within Firewall even think that the TITANs may not have been
   responsible for the Pandora Gates ... They have a name for this mystery
   infection. They call it the Exsurgent virus.
\end{quote}

\begin{quote}
   \textbf{Criminal factions}

   Where there is humanity, there will be an underworld and the organizations
   that run it. The following are a sample of the major players.


   \textbf{Triads}

   The only syndicate that survived the Fall almost unscathed, the Triads
   dominate the solar system's underworld by their sheer membership size and
   a history of centuries of economic and political influence. Having
   evolved into legit enterprises and small economic consortiums before the
   Fall, the Triads had the resources to ensure their survival during the
   evacuation from Earth and the connections throughout all major habitats
   to gain a foothold early on in the colonization of space.


   \textbf{Night Cartel} 

   Progressive in both entrepreneurial and criminal vision, the Night Cartel
   emerged from the remnants of Earth's underworld syndicates, merging the
   best qualities of each. Depending on the field of operations, the Night
   Cartel even holds legitimate hypercorp status in certain habitats, while
   working outside the law elsewhere. The Night Cartel is involved in all
   kinds of criminal activity, from traditional racketeering, extortion, and
   prostitution to nanofabber piracy, electronic stimulants, and designer
   drugs.


   \textbf{Intelligent Design Crew (ID-Crew)}

   The ID crew specializes in electronic crimes and information brokerage,
   including credit and rep fraud, identity counterfeiting, and datatheft.
   The ID crew is believed to have grown from several hacker gangs assimilated
   under the leadership of an infomorph consortium. Due to its service sector,
   the ID crew maintains a minimalist physical profile, but can be found in
   almost any habitat's or station's mesh.


   \textbf{Nine Lives}

   This widespread network of soul-traders specializes in the acquisition and
   trafficking of transhuman egos. Stealing backups, forknapping, and
   intercepting egocasts are all part of their repertoire. Nine Lives are
   known to run illegal fork-slave colonies as well as organize pit fights
   with all manner of physical bodies (synthetic shells, pods, uplifts, smart
   animals) and all manner of egos (human, AI, animal, etc).
\end{quote}

\begin{quote}
   \textbf{INFORMATION AT YOUR FINGERTIPS}

   The following information is always available for most meshers in a normal
   habitat or city.


   \textbf{Local conditions}
   \begin{itemize}
      \item Local maps showing your current location, annotated with local
         features of personal interest (according to your personal preferences
         and filters) and your distance from them/directions to them. Details
         regarding private and restricted areas (government/hypercorp areas,
         maintenance/security infrastructure, etc.) are usually not included.

      \item Current habitat life support (climate) conditions, including
         atmosphere composition and temperature.

      \item Current solar system and habitat orbit map with trajectory plots
         and communication delays.
   \end{itemize}


   \textbf{Local mesh}
   \begin{itemize}
      \item Public search engines, databases, mesh sites, blogs, forums, and
         archives, along with new content alerts.
      \item Syndicated newsfeeds in a variety of formats, filtered according
         to your preferences.
      \item Sensor feeds from any public area of the habitat.
      \item Automatic searches for new online references to your name and other
         subjects of interest.
      \item Facial/image recognition searches of public mesh/archives to
         match a photo/vid still.
   \end{itemize}


   \textbf{Personal information}
   \begin{itemize}
      \item Morph status indicators (medical and/or mechanical): blood
         pressure, heart rate, temperature, white cell count, nutrient
         levels, implant status and functionality, etc.
      \item Location, functionality, sensor feeds, and status reports of
         your possessions (via sensors and transmitters in these possessions).
      \item Access to one's life-spanning personal audio-visual/XP archive.
      \item Access to one's life-spanning personal file archive (music,
         software, media, documents, etc.).
      \item Reputation score, social network status, and credit account
         status.
   \end{itemize}
\end{quote}


